Incentivizing Exploration with Unbiased History

### 2018-11-01 2level.tex
Removed proof sketch.
More minor edits.

\begin{proof}[Proof Sketch]
\ascomment{Jieming, pls add a brief proof sketch if you can.}
\jmcomment{The main idea of the proof is to consider the case when all pulled arms have bad realized rewards (i.e. 0). }
\jmcomment{Actually, not clear about how to write a sketch for a proof of 8 lines.}
\end{proof}

@@

It is useful to think of the info-graph as having two levels (corresponding to exploration and exploitation). Accordingly, we call this policy the \emph{\2LEVEL}. We show that it incentivizes the agents to perform non-adaptive exploration, and achieves a regret rate of  $\tilde O_K(T^{2/3})$. The key idea is that using many full-disclosure paths ``in parallel" ensures that sufficiently many samples of each arm are collected during exploration.

>>>>

\OMIT{ %%%%%%
\begin{proof}[Proof Sketch]
\ascomment{Jieming, pls add a brief proof sketch if you can.}
\jmcomment{The main idea of the proof is to consider the case when all pulled arms have bad realized rewards (i.e. 0). }
\jmcomment{Actually, not clear about how to write a sketch for a proof of 8 lines.}
\end{proof}
} %%%%%%

@@

The info-graph has two ``levels", corresponding to exploration and exploitation. Accordingly, we call this policy the \emph{\2LEVEL}. We show that it incentivizes the agents to perform non-adaptive exploration, and achieves a regret rate of  $\tilde O_K(T^{2/3})$. The key idea is that since one full-disclosure path collects one sample of a given arm with constant probability, using many full-disclosure paths ``in parallel" ensures that sufficiently many samples of this arm are collected.
